Classless Java: Tuning Java Interfaces

### 2015-12-06 paper/sections/Formalization.tex
Now needed is good, (lets hope). I think it passes the H example!

Defining \mBody{} is not trivial, and requires quite a lot of attention to the specific model of Java Interfaces, and on how it differs w.r.t. Java Class model.
$\mBody(\m,\C)$ denotes the actual method $\m$ (body included) that
interface $\C$ owns. The method can either be defined originally in $\C$ or in its supertypes, and then passed to $\C$ via inheritance.
\noindent$\begin{array}{l}
\InTextDef{15ex}{
\mBody(\m,\C_0)
}{
\override(\methods(\m),
\shadow(\tops(\m,\C_0)))
}\\
\InTextWith{\metaVar{IT}(\C_0) =
\ \ann\ \QM{interface}\ \C_0\ \QM{extends}\ \Cs\ \oC\methods\ \cC}
\end{array}$

\noindent The definition of $\mBody$ delegates the work to three others auxiliary functions:
 $\tops(m,\C_0)$, $\shadow(\methods)$ and $\override(\method,\method')$.

\paragraph{\tops{}} recovers from the interface table only the ``needed'' methods, that is,
the non-static ones that are not transitively reachable by following another, less specific, superinterface chain.
\hl{Another two functions $\super(\C_0)$ and $\get(\m,\C_0)$ are used for the definition. $\super(\C_0)$ collects the
super interfaces of $\C_0$ recursively, and $\get(\m,\C_0)$ returns the non-static method declared in $\C_0$ with name $\m$, or $\emptyset$ otherwise.
Finally, $\tops(\m,\C_0)$ returns the topmost methods $m$ from the super interfaces.}
Formally:

\noindent$\begin{array}{l}
\InTextDef{13ex}{
\tops(\m,\C_0)}{
}{
\{\ \get(\m, \C)\ |\ \C\in\super(\C_0), \get(\m, \C) \ne\emptyset,\mbox{ and }
}\\
\hspace{2.1in}\forall\C'\in\super(\C_0)\mbox{ and }\get(\m,\C')\ne\emptyset: \C'<:\C\Rightarrow\C'=\C\ \}\\
\InTextDef{13ex}{
\super(\C_0)}{
}{
\{\ \C'\ |\ \C'\in\Cs,\mbox{ or }\exists\C\in\Cs,\C'\in\super(\C)\ \}
}\\
\InTextWith{\metaVar{IT}(\C_0) =
\ \ann\ \QM{interface}\ \C_0\ \QM{extends}\ \Cs\ \oC\methods\ \cC}\\
\InTextDef{13ex}{
\get(\m,\C_0)}{
}{
\method
}\\
\InTextWith{\metaVar{IT}(\C_0) =
\ \ann\ \QM{interface}\ \C_0\ \QM{extends}\ \Cs\ \oC\methods\ \cC, \method\in\methods\mbox{ not static},\m=\m^\method}
\end{array}$

>>>>

Defining \mBody{} is not trivial, and requires quite a lot of attention to the specific model of Java Interfaces, and on how it differs w.r.t. Java Class model.
$\mBody(\m,\C)$ denotes the actual method $\m$ (body included) that
interface $\C$ owns. The method can either be defined originally in $\C$ or in its supertypes, and then passed to $\C$ via inheritance.
\noindent$\begin{array}{l}
\InTextDef{15ex}{
\mBody(\m,\C_0)
}{
\override(\methods(\m),
\shadow(\tops(\m,\Cs)))
}\\
\InTextWith{\metaVar{IT}(\C_0) =
\ \ann\ \QM{interface}\ \C_0\ \QM{extends}\ \C_1\ldots\C_n\ \oC\methods\ \cC \mbox{ and }
 \C\in\Cs \mbox{ if } \C_i\subtype\C, i\in 1..n

}
\end{array}$

\noindent The definition of $\mBody$ reconstruct the full set of supertypes $\Cs$ and then delegates the work to three others auxiliary functions:
 $\tops(m,\C_0)$, $\shadow(\methods)$ and $\override(\method,\method')$.

\paragraph{\tops{}} recovers from the interface table only the ``needed'' methods, that is,
the non-static ones that are not reachable by another, less specific, superinterface.
Since the second parameter of \tops{} is a set, we can choose an arbitrary element to be $\C_0$.
%\hl{Another two functions $\super(\C_0)$ and $\get(\m,\C_0)$ are used for the definition. $\super(\C_0)$ collects the
%super interfaces of $\C_0$ recursively, and $\get(\m,\C_0)$ returns the non-static method declared in $\C_0$ with name $\m$, or $\emptyset$ otherwise.
%Finally, $\tops(\m,\C_0)$ returns the topmost methods $m$ from the super interfaces.}
Formally:

\noindent$\begin{array}{l}
\InTextDef{27ex}{
\method\in\tops(\m,\C_0\dots\C_n)}{
 }{
\metaVar{IT}(\C_0)(\m)=\method,  \method\mbox{ default or abstract method}
 }\\
\InTextWith{
\not\exists i\in1..n \mbox{ such that } 
\metaVar{IT}(\C_i)(\m)\mbox{ is a default or abstract method, and }
\C_i \subtype \C_0}

%\\
%\InTextDef{13ex}{
%\tops(\m,\C_0)}{
%}{
%\{\ \get(\m, \C)\ |\ \C\in\super(\C_0), \get(\m, \C) \ne\emptyset,\mbox{ and }
%}\\
%\hspace{2.1in}\forall\C'\in\super(\C_0)\mbox{ and }\get(\m,\C')\ne\emptyset: \C'<:\C\Rightarrow\C'=\C\ \}\\
%\InTextDef{13ex}{
%\super(\C_0)}{
%}{
%\{\ \C'\ |\ \C'\in\Cs,\mbox{ or }\exists\C\in\Cs,\C'\in\super(\C)\ \}
%}\\
%\InTextWith{\metaVar{IT}(\C_0) =
%\ \ann\ \QM{interface}\ \C_0\ \QM{extends}\ \Cs\ \oC\methods\ \cC}\\
%\InTextDef{13ex}{
%\get(\m,\C_0)}{
%}{
%\method
%}\\
%\InTextWith{\metaVar{IT}(\C_0) =
%\ \ann\ \QM{interface}\ \C_0\ \QM{extends}\ \Cs\ \oC\methods\ \cC, \method\in\methods\mbox{ not static},\m=\m^\method}
\end{array}$
